### 2021-09-08 input/proposal.tex
wip

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every \process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \process eventually
    delivers and forwards the best up-to-date delivered messages.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together as
  in Theorem~\ref{theo:bef}.
\end{proof}

@@

Algorithm~\ref{algo:ascast} provides the few instructions of \NAME
that implement three-phase purge and best eventual forwarding to
enable dynamic consistent partitioning. For the sake of simplicity, it
does not handle multiple sessions and associated optimisation such as
data structure sharing and message packing.

@@

As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
not only requires eventual purging of stale control information, but
also the retrieval of the best up-to-date partitions.  In that regard,
both $\delta$ and $\Delta$ messages have dual use: since they already
reach the borders of their partition by design, they also trigger a
competition when reaching such bordering \processes (see
Line~\ref{line:ascast_compete}).
%% This simply consists in sending the
%% current partition through the communication link from which the
%% \process received the $\delta$. Upon receipt of this answer,
%% \processes act normally by propagating their changes when they
%% improve.

>>>>

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    upon receipt of such $\alpha_y$, either the \process already 
    \TODO{tododododotododoo.}

    ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
    S(\alpha_y)$)

    eventually every \process only delivers and forwards up-to-date
    messages, or no message at all ($\eventually d_c(m') \implies \neg
    S(m')$).

    , every \process eventually delivers and forwards the best
    up-to-date delivered messages as in Theorem~\ref{theo:bef}.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together.
\end{proof}

@@

Algorithm~\ref{algo:ascast} provides the few instructions of \NAME
that implement three-phase purge and eventual forwarding of best to
enable dynamic consistent partitioning. For the sake of simplicity, it
does not handle multiple sessions and associated optimisation such as
data structure sharing and message packing.

@@

As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
not only requires eventual purging of stale messages, but also the
retrieval of the best up-to-date partitions.  In that regard, both
$\delta$ and $\Delta$ messages have dual use: since they already reach
the borders of their partition by design, they trigger a competition
when reaching bordering \processes (see
Line~\ref{line:ascast_compete}).
%% This simply consists in sending the
%% current partition through the communication link from which the
%% \process received the $\delta$. Upon receipt of this answer,
%% \processes act normally by propagating their changes when they
%% improve.
